\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[margin=1.25in]{geometry}
\usepackage{pdfpages}

\usepackage{listings}
\usepackage{color}
\usepackage{graphicx}


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
 
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}


\lstset{
  tabsize=4,
  language=c++,
  style = mystyle
}

\title{CS290 (Winter 2018) - Project Proposal}
\author{Marc Tibbs (tibbsm@oregonstate.edu)}
\date{Due Date: February 18, 2018}

\begin{document}

\maketitle

I am planning to make a personal website for this project as a hub for showing my work. While my overall plan is to make a simple and minimalistic site, this project will allow me to tinker with the basics of website design and experiment with different designs for my personal website. I have listed the basic design concepts that I have so far for my website. 

\section*{Structure:}

The website will initially include total of four different pages. 

\begin{itemize}
    \item The \textbf{homepage} will have a picture carousel animation that will display some of the highlights of my work. 
    \item The \textbf{about me} page will include a short bio on myself and have my resume on display and available for download. 
    \item The \textbf{notes} page will contain a running journal of ideas that I have. 
    \item The \textbf{sketches} page will act as a running catalog of the pictures and ideas that I sketch out. 
\end{itemize}

\section*{Layout:}

The layout of the pages will be simple and consistent with one another. In general each page will have:
\begin{itemize}
    \item The \textbf{header} will contain a navigation bar with links to each page. 
    \item The \textbf{body} of the page will include the main content of the page. For example, the resume page will display my resume. 
    \item The \textbf{footer} of the page will include links to my various social media profiles, such as, linkedIn, Instagram, etc.
\end{itemize}

\section*{Theme:}

In terms of theme, I would like my website to have a simple design. The majority of the site will be black and white and will use color sparingly to highlight key points. 

\newpage
\section*{Project Requirements:}

\begin{itemize}[leftmargin=1cm]
	\item \textbf{The webpages should be presentable as a whole; the interface should be user friendly (text should be easy to read); the website should contain pictures or videos.}
	\begin{itemize}
        \item The website will have a overall design to tie it all together. I plan to the same structure for each of the page so that the whole site has a cohesive design. 
        \item The website will focus on simple design which will lead to a user friendly design.
        \item The website will include mostly pictures at this point. I have no desire to add videos at this time, but keep the option open for the future.
    \end{itemize}
	
    \item \textbf{Website has 1 homepage and at least 3 subpages; the homepage and subpages have a horizontal menu that leads to the other pages.}
	\begin{itemize}
        \item The website will initially be designed to have one homepade and 3 subpages. 
        \item All the pages will be reachable from the navigation bar in the header of each page.
    \end{itemize}

    \item \textbf{The homepage has picture carousel animation (slideshow effect, for example, pictures in this page http://oregonstateparks.org.}
    \begin{itemize}
        \item The homepage will have a picture carousel animation highlighting my most recent work. 
    \end{itemize}

	\item \textbf{Have a scroll box in one page. You can put anything inside the scroll box.}
    \begin{itemize}
        \item I will have a scroll box on the "about" page to contain my resume. 
    \end{itemize}

	\item \textbf{One page has unordered HTML list with several entries.}
    \begin{itemize}
        \item The "about" page will also contain an unordered list as part of my short bio.
    \end{itemize}

	\item \textbf{There is a button to download files (map to the farm, menu in the restaurant, a personal CV, etc.) The downloaded file can either open in the browser or download to the local computer.}
    \begin{itemize}
        \item There will be a button to download my resume on the "about" page. 
    \end{itemize}

	\item \textbf{There is a link that you can click and leads to outside webpages (linkedin, yelp, email, etc.)}
    \begin{itemize}
        \item The footer of each page will contain links to my personal social media pages. 
    \end{itemize}

\end{itemize}


\end{document}
